---
title: "Mestrado"
author: "David Ferreira Quaresma (david.quaresma@ccc.ufcg.edu.br)"
date: "ago, 2025"
output: pdf_document
---

# Load Functions
```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
##require(quantileCI)

load_data <- function(results_path, techs, probs, idletimes) {
  all_invocs <- list()
  all_replicas <- list()
  for (t in techs) {
    for (p in probs) {
      for (i in idletimes) {
        scenario = paste(t, i, p, sep = "_")
        fileName = paste(scenario, "-invocations.csv", sep="")
        df_invocs = read.csv(paste(results_path, t, fileName, sep="/"), header = TRUE)
        df_invocs$minResponseTime = pmin(df_invocs$responseTime, df_invocs$techniqueResponseTime)
        df_invocs$responseTimeToEvaluate = ifelse(
          df_invocs$minResponseTime != 0,
          df_invocs$minResponseTime,
          df_invocs$responseTime
        )
        df_invocs$technique = t
        df_invocs$idletime = i
        df_invocs$tailLatencyProb = p

        df_invocs <- df_invocs %>%
          group_by(funcID) %>%
          mutate(
            p50  = quantile(responseTimeToEvaluate, probs = 0.50, na.rm = TRUE),
            p95  = quantile(responseTimeToEvaluate, probs = 0.95, na.rm = TRUE),
            p99  = quantile(responseTimeToEvaluate, probs = 0.99, na.rm = TRUE),
            p999 = quantile(responseTimeToEvaluate, probs = 0.999, na.rm = TRUE),
            p100 = quantile(responseTimeToEvaluate, probs = 1.00, na.rm = TRUE)
          ) %>%
          ungroup()

        df_invocs <- df_invocs %>% distinct(funcID, .keep_all = TRUE)
        all_invocs[[length(all_invocs) + 1]] <- data.frame(
          funcID          = df_invocs$funcID,
          technique       = df_invocs$technique,
          tailLatencyProb = df_invocs$tailLatencyProb,
          idletime        = df_invocs$idletime,
          p50             = df_invocs$p50,
          p95             = df_invocs$p95,
          p99             = df_invocs$p99,
          p999            = df_invocs$p999,
          p100            = df_invocs$p100
        )

        fileName = paste(scenario, "-replicas.csv", sep="")
        df_replicas = read.csv(paste(results_path, t, fileName, sep="/"), header = TRUE)
        df_replicas$technique = t
        df_replicas$idletime = i
        df_replicas$tailLatencyProb = p
        df_replicas$replicasCount = nrow(filter(df_replicas, funcID == df_replicas$funcID))
        df_replicas <- df_replicas %>%
          group_by(funcID) %>%
          mutate(
            totalUptime = sum(df_replicas$upTime) /1000/60/60,
            totalBusyTime = sum(df_replicas$busyTime) /1000/60/60,
          ) %>%
        ungroup()
        

        df_replicas <- df_replicas %>% distinct(funcID, .keep_all = TRUE)
        all_replicas[[length(all_replicas) + 1]] <- data.frame(
          funcID          = df_replicas$funcID,
          technique       = df_replicas$technique,
          tailLatencyProb = df_replicas$tailLatencyProb,
          idletime        = df_replicas$idletime,
          totalUptime     = df_replicas$totalUptime,
          totalBusyTime   = df_replicas$totalBusyTime,
          replicasCount   = df_replicas$replicasCount
        )
      }
    }
  }
  df_for_invocs <- parse_idletime_and_probs(do.call(rbind, all_invocs))
  df_for_replicas <- parse_idletime_and_probs(do.call(rbind, all_replicas))
  return(list(df_for_invocations = df_for_invocs, df_for_replicas = df_for_replicas))
}

parse_idletime_and_probs <- function(df) {
  df$tailLatencyProb = ifelse(df$tailLatencyProb == "tlprobp95", 95, df$tailLatencyProb)
  df$tailLatencyProb = ifelse(df$tailLatencyProb == "tlprobp99", 99, df$tailLatencyProb)

  df$idletime = ifelse(df$idletime == "idletime0.0", 0, df$idletime)
  df$idletime = ifelse(df$idletime == "idletime900.0", 900, df$idletime)
  df$idletime = ifelse(df$idletime == "idletimeINF", Inf, df$idletime)

  return(df)
}
```

# Load Data Grouping All Simulation Scenarios
```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
#results_path <- "/Users/davidquaresma/Desktop/repos/faas-simulator/results_azure"
results_path <- "/Users/davidquaresma/Desktop/repos/faas-simulator/results_generator"
techs <- c('RequestHedgingOpt', 'Vanilla', 'GCI', 'RequestHedgingDefault')
probs <- c('tlprobp95', 'tlprobp99')
idletimes <- c('idletimeINF', 'idletime0.0', 'idletime900.0')

start_time <- Sys.time()
data_loaded <- load_data(results_path, techs, probs, idletimes)
df_for_invocations <- data_loaded$df_for_invocations
df_for_replicas <- data_loaded$df_for_replicas
end_time <- Sys.time()
print(paste("All Azure Simulation Load Time: ", end_time - start_time, sep=""))

rm(data_loaded)
```

# Load Plot Functions
```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
plot_hist_results <- function(df, metric, y_label, title) {
  df$idletime_f <- factor(df$idletime, levels = c(0, 900, Inf))
  ggplot(df, aes(x=tailLatencyProb, y=metric, color=as.factor(technique), shape=as.factor(technique))) +
    geom_jitter(width = 0.015, height = 0, alpha = 0.8, size = 2.5, stroke = 1) +
    facet_grid(. ~ factor(idletime_f, levels = c(0, 900, Inf))) +
    labs(x = "tail latency probability", y = y_label, title = title, colour = "technique", shape = "technique") +
    scale_shape_manual(values = c(1, 23, 24, 15)) +
    scale_color_manual(values = c("red", "purple", "blue", "limegreen")) +  # cores mais distintas
    theme_bw() +
    theme(
      legend.position = "bottom",
      strip.text = element_text(size = 12),
      axis.text = element_text(size = 10)
    )
}

plot_ecdf <- function(title, data, xinf, xsup, yinf, ysup, linetype=c("solid", "dotted", "dotdash", "dashed"), cols=c(15, 195, 150), img_name=FALSE) {
    vanilla.color <- "limegreen"
    vanilla.p95 <- quantile(data$vanilla, 0.95)
    vanilla.p999 <- quantile(data$vanilla, 0.999)
    vanilla.p50 <- quantile(data$vanilla, 0.5)

    rh.color <- "purple"
    rh.p95 <- quantile(data$rh, 0.95)
    rh.p999 <- quantile(data$rh, 0.999)
    rh.p50 <- quantile(data$rh, 0.5)
    
    rho.color <- "blue"
    rho.p95 <- quantile(data$rho, 0.95)
    rho.p999 <- quantile(data$rho, 0.999)
    rho.p50 <- quantile(data$rho, 0.5)

    gci.color <- "red"
    gci.p95 <- quantile(data$gci, 0.95)
    gci.p999 <- quantile(data$gci, 0.999)
    gci.p50 <- quantile(data$gci, 0.5)

    # Definindo alturas diferentes para cada grupo
    vanilla_y = 0.9
    rh_y = 0.1
    rho_y = 0.7
    gci_y = 0.4
    
    size = 0.5
    alpha = 0.8
    angle = 90
    
    p <- data[, colSums(is.na(data)) != nrow(data)] %>%
    pivot_longer(everything()) %>%
    group_by(name) %>%
    arrange(value, by_group = TRUE) %>%
    mutate(ecdf = seq(1/n(), 1 - 1/n(), length.out = n())) %>%
    ggplot(aes(x = value, y = ecdf, colour=name, linetype=name)) +
    xlim(xinf, xsup) +
    ylim(yinf, ysup) +
    geom_step() +
    theme(text=element_text(size=12), plot.title = element_text(hjust = 0.5))+
    theme(legend.text=element_text(size=12)) +
    theme(legend.position="top") +

    scale_color_manual(values=c("vanilla"="limegreen", "rh"="purple", "rho"="blue", "gci"="red")) +
    scale_fill_manual(values=hcl(100, 65, alpha=c(1, 1, 1, 1))) +
    scale_linetype_manual(values=c("vanilla"="solid", "rh"="dotted", "rho"="dotdash", "gci"="dashed")) +
    labs(x="Response Time (ms)",y="ECDF", color="scenario", linetype="scenario") +
    ggtitle(title) +

    # Vanilla annotations - todos na mesma altura do grupo vanilla
    annotate(geom="text", x=vanilla.p50, y=vanilla_y, label="Median", angle=angle, color=vanilla.color) +
    geom_vline(xintercept=vanilla.p50, linetype="solid", size=size, alpha=alpha, color=vanilla.color) +
    annotate(geom="text", x=vanilla.p95, y=vanilla_y, label="95th", angle=angle, color=vanilla.color) +
    geom_vline(xintercept=vanilla.p95, linetype="solid", size=size, alpha=alpha, color=vanilla.color) +
    annotate(geom="text", x=vanilla.p999, y=vanilla_y, label="99.9th", angle=angle, color=vanilla.color) +
    geom_vline(xintercept=vanilla.p999, linetype="solid", size=size, alpha=alpha, color=vanilla.color) +

    # RH annotations - todos na mesma altura do grupo rh
    annotate(geom="text", x=rh.p50, y=rh_y, label="Median", angle=angle, color=rh.color) +
    geom_vline(xintercept=rh.p50, linetype="dotted", size=size, alpha=alpha, color=rh.color) +
    annotate(geom="text", x=rh.p95, y=rh_y, label="95th", angle=angle, color=rh.color) +
    geom_vline(xintercept=rh.p95, linetype="dotted", size=size, alpha=alpha, color=rh.color) +
    annotate(geom="text", x=rh.p999, y=rh_y, label="99.9th", angle=angle, color=rh.color) +
    geom_vline(xintercept=rh.p999, linetype="dotted", size=size, alpha=alpha, color=rh.color) +

    # RHO annotations - todos na mesma altura do grupo rho
    annotate(geom="text", x=rho.p50, y=rho_y, label="Median", angle=angle, color=rho.color) +
    geom_vline(xintercept=rho.p50, linetype="dotdash", size=size, alpha=alpha, color=rho.color) +
    annotate(geom="text", x=rho.p95, y=rho_y, label="95th", angle=angle, color=rho.color) +
    geom_vline(xintercept=rho.p95, linetype="dotdash", size=size, alpha=alpha, color=rho.color) +
    annotate(geom="text", x=rho.p999, y=rho_y, label="99.9th", angle=angle, color=rho.color) +
    geom_vline(xintercept=rho.p999, linetype="dotdash", size=size, alpha=alpha, color=rho.color) +

    # GCI annotations - todos na mesma altura do grupo gci
    annotate(geom="text", x=gci.p50, y=gci_y, label="Median", angle=angle, color=gci.color) +
    geom_vline(xintercept=gci.p50, linetype="dashed", size=size, alpha=alpha, color=gci.color) +
    annotate(geom="text", x=gci.p95, y=gci_y, label="95th", angle=angle, color=gci.color) +
    geom_vline(xintercept=gci.p95, linetype="dashed", size=size, alpha=alpha, color=gci.color) +
    annotate(geom="text", x=gci.p999, y=gci_y, label="99.9th", angle=angle, color=gci.color) +
    geom_vline(xintercept=gci.p999, linetype="dashed", size=size, alpha=alpha, color=gci.color) +

    theme_bw()
        
    if (img_name != FALSE) {
      ggsave(img_name, width=10, height=5)
    }
    print(p)
}

plot_boxplot <- function(title, df_a, df_b, df_c, df_d, yrange, outliershape = NA) {
  return(ggplot(rbind(df_a, df_b, df_c, df_d), aes(x=scenario, y=responseTime, fill=scenario)) +
  geom_boxplot(outlier.shape = outliershape) +
  scale_fill_manual(values = c("red", "purple", "blue", "limegreen")) +
  coord_cartesian(ylim=yrange) + 
  theme(text=element_text(size=15)) +
  theme(legend.text=element_text(size=15)) +
  labs(x = "scenario", y = "latency (ms)") +
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank(), plot.title = element_text(hjust = 0.5)) +
  theme_bw() +
  ggtitle(title)
  )
}

plot_replicas_alive <- function(data, scenario_col = "scenario", title = "Replicas Active") {
  data$time_readable <- as.POSIXct(data$timestamp, origin = "2021-01-31", tz = "UTC")
  data[[scenario_col]] <- factor(
    data[[scenario_col]],
    levels = c("gci", "rh", "rho", "vanilla")
  )
  
  ggplot(data, aes(x = time_readable, y = replica_amount, color = !!sym(scenario_col))) +
    geom_line(size = 0.5) +
    geom_point(size = 0.5) +
    scale_color_manual(values=c("vanilla"="limegreen", "rh"="purple", "rho"="blue", "gci"="red")) +
    scale_fill_manual(values=hcl(100, 65, alpha=c(1, 1, 1, 1))) +
    scale_linetype_manual(values=c("vanilla"="solid", "rh"="dotted", "rho"="dotdash", "gci"="dashed")) +
    scale_x_datetime(
      date_labels = "%d %b\n%H:%M",   # e.g. "01 Jan\n12:00"
      date_breaks = "2 days"          # tick every 2 days
    ) +
    labs(
      title = title,
      x = "Time (2-week window)",
      y = "Amount of Alive Replicas",
      color = "scenario"
    ) +
    theme_minimal(base_size = 14) +
    theme(
      plot.title = element_text(hjust = 0.5, face = "bold"),
      legend.position = "top"
    )
}

plot_requests_workload <- function(data, bin_size = "10 min", title = "Requests Over Time") {
  data$time_readable <- as.POSIXct(data$target_timestamp, origin = "2021-01-31", tz = "UTC")
  binned_data <- data %>%
    mutate(bin_time = cut(time_readable, breaks = bin_size)) %>%
    group_by(bin_time) %>%
    summarise(requests = n(), .groups = "drop") %>%
    mutate(bin_time = as.POSIXct(bin_time, tz = "UTC"))

  ggplot(binned_data, aes(x = bin_time, y = requests)) +
    geom_line(color = "steelblue", size = 1) +
    geom_point(color = "steelblue", size = 1) +
    scale_x_datetime(
      date_labels = "%d %b\n%H:%M",
      date_breaks = "2 days"
    ) +
    labs(
      title = title,
      x = "Time (2-week window)",
      y = "Amount of Invocations"
    ) +
    theme_minimal(base_size = 14) +
    theme(
      plot.title = element_text(hjust = 0.5, face = "bold"),
      legend.position = "none"
    )
}
```

# Plot Hist For Invocations/Replicas For All Azure Scenarios
```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
functions_to_plot <- c(
  "155e47f8e7f751d0c845049456d01832013c61336a8cd85901330ac821a71534", # 535667 -> 535667
  "8ef9c2c907e9cd5fb4b5cb3bfbebca6d9a01bb1f65a0f476e3914cae25bd2aae", # 212755 -> 161085 (had zero duration entries)
  "cc5bb2108cc7daf53f9728ad21f661a8ef9c8b36284bacfcb712e2be87eef842", # 142856 -> 142856
  "4753d9ffc8a362eadfb27498581969561c0ddbec7257759dbcb9936e506aff82", # 124143 -> 124143
  "89d488538f940c98367ff572230106d1089868bdd379d9e2b9755b679dc186d2", # 76093 -> 76093
  "bd5be891d0d10fbc3c59215d5f8159ea496433bc41adba7d8d10ea21d35c3e3a", # 116130 -> 73464 (had zero duration entries)
  "30aa434528bc68ee07745ee7be3a0bdb33d58961fdc8460ce5b5b46b4def96e8", # 71759 -> 71759
  "b89efb5e9d1b7e5900ef441b098d4c8b01600af5e673a9f9d607b3598f0fe548", # 63506 -> 63506
  "8e5f533dbf1092f56ac6c7542ef3bdec4661bd442c9b5e7537fabc7b8c03f5a8", # 53263 -> 53263
  "c098bb74acb70a0ea1bce98a7090169f3be59a0758389a403d77592aa56ce596", # 41333 -> 41333
  "eefb3a7b86d12c2676276a5dde28099ef6f546a60e5b78e0a1c2b7221baf154d"  # 41333 -> 3107 (had too many zero duration entries)
)
  
titles <- c(
  "func w/ suffix 534",
  "func w/ suffix aae", 
  "func w/ suffix 842",
  "func w/ suffix f82",
  "func w/ suffix 6d2",
  "func w/ suffix e3a", 
  "func w/ suffix 6e8",
  "func w/ suffix 548",
  "func w/ suffix 5a8",
  "func w/ suffix 596",
  "func w/ suffix 54d"
)

selected_func = functions_to_plot[11]

invocs_to_plot = filter(df_for_invocations, funcID == selected_func)
plot_hist_results(
  invocs_to_plot,
  invocs_to_plot$p95,
  "response time (ms)", "95th of invocations' response time for each idletime"
)
plot_hist_results(
  invocs_to_plot[invocs_to_plot$idletime != 0, ],
  invocs_to_plot[invocs_to_plot$idletime != 0, ]$p95,
  "response time (ms)", "95th of invocations' response time for each idletime (excluding idletime zero)"
)

plot_hist_results(
  invocs_to_plot,
  invocs_to_plot$p99,
  "response time (ms)", "99th of invocations' response time for each idletime"
)
plot_hist_results(
  invocs_to_plot[invocs_to_plot$idletime != 0, ],
  invocs_to_plot[invocs_to_plot$idletime != 0, ]$p99,
  "response time (ms)", "999th of invocations' response time for each idletime (excluding idletime zero)"
)

plot_hist_results(
  invocs_to_plot,
  invocs_to_plot$p999,
  "response time (ms)", "999th of invocations' response time for each idletime"
)
plot_hist_results(
  invocs_to_plot[invocs_to_plot$idletime != 0, ],
  invocs_to_plot[invocs_to_plot$idletime != 0, ]$p999,
  "response time (ms)", "999th of invocations' response time for each idletime (excluding idletime zero)"
)

replicas_to_plot = filter(df_for_replicas, funcID == selected_func)
plot_hist_results(
  replicas_to_plot,
  replicas_to_plot$totalUptime,
  "total uptime (hour)", "Total replicas TotalUpTime for each idletime"
)
plot_hist_results(
  replicas_to_plot[replicas_to_plot$idletime != Inf, ],
  replicas_to_plot[replicas_to_plot$idletime != Inf, ]$totalUptime,
  "total uptime (hour)", "Total replicas TotalUpTime for each idletime (excluding idletime Inf)"
)

plot_hist_results(
  replicas_to_plot,
  replicas_to_plot$totalBusyTime,
  "total busy-time (hour)", "Total replicas TotalBusyTime for each idletime"
)
plot_hist_results(
  replicas_to_plot[replicas_to_plot$idletime != 0, ],
  replicas_to_plot[replicas_to_plot$idletime != 0, ]$totalBusyTime,
  "total busy-time (hour)", "Total replicas TotalBusyTime for each idletime (excluding idletime zero)"
)

plot_hist_results(
  replicas_to_plot,
  replicas_to_plot$totalBusyTime / replicas_to_plot$totalUptime,
  "total busy-time (hour)", "Total replicas Efficiency for each idletime"
)
plot_hist_results(
  replicas_to_plot[replicas_to_plot$idletime != 0, ],
  replicas_to_plot[replicas_to_plot$idletime != 0, ]$totalBusyTime / replicas_to_plot[replicas_to_plot$idletime != Inf, ]$totalUptime,
  "total busy-time (hour)", "Total replicas Efficiency for each idletime (excluding idletime zero)"
)

plot_hist_results(
  replicas_to_plot,
  replicas_to_plot$replicasCount,
  "number of replicas", "Total number of replicas created for each idletime"
)
plot_hist_results(
  replicas_to_plot[replicas_to_plot$idletime != 0, ],
  replicas_to_plot[replicas_to_plot$idletime != 0, ]$replicasCount,
  "number of replicas", "Total number of replicas created for each idletime (excluding idletime zero)"
)
```

# Plot Hist For Invocations/Replicas For All Azure Scenarios
```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
functions_to_plot <- c(
  "constant-bernoulli-func",
  "poisson-bernoulli-func",
  "constant-weibull-func",
  "poisson-weibull-func",
  "constant-logNormal-func",
  "poisson-logNormal-func"
)
  
titles <- c(
  "func constant-bernoulli",
  "func poisson-bernoulli",
  "func constant-weibull",
  "func poisson-weibull",
  "func constant-logNormal",
  "func poisson-logNormal"
)

selected_func = functions_to_plot[4]

invocs_to_plot = filter(df_for_invocations, funcID == selected_func)
plot_hist_results(
  invocs_to_plot,
  invocs_to_plot$p95,
  "response time (ms)", "95th of invocations' response time for each idletime"
)
plot_hist_results(
  invocs_to_plot[invocs_to_plot$idletime != 0, ],
  invocs_to_plot[invocs_to_plot$idletime != 0, ]$p95,
  "response time (ms)", "95th of invocations' response time for each idletime (excluding idletime zero)"
)

plot_hist_results(
  invocs_to_plot,
  invocs_to_plot$p99,
  "response time (ms)", "99th of invocations' response time for each idletime"
)
plot_hist_results(
  invocs_to_plot[invocs_to_plot$idletime != 0, ],
  invocs_to_plot[invocs_to_plot$idletime != 0, ]$p99,
  "response time (ms)", "999th of invocations' response time for each idletime (excluding idletime zero)"
)

plot_hist_results(
  invocs_to_plot,
  invocs_to_plot$p999,
  "response time (ms)", "999th of invocations' response time for each idletime"
)
plot_hist_results(
  invocs_to_plot[invocs_to_plot$idletime != 0, ],
  invocs_to_plot[invocs_to_plot$idletime != 0, ]$p999,
  "response time (ms)", "999th of invocations' response time for each idletime (excluding idletime zero)"
)

replicas_to_plot = filter(df_for_replicas, funcID == selected_func)
plot_hist_results(
  replicas_to_plot,
  replicas_to_plot$totalUptime,
  "total uptime (hour)", "Total replicas TotalUpTime for each idletime"
)
plot_hist_results(
  replicas_to_plot[replicas_to_plot$idletime != Inf, ],
  replicas_to_plot[replicas_to_plot$idletime != Inf, ]$totalUptime,
  "total uptime (hour)", "Total replicas TotalUpTime for each idletime (excluding idletime Inf)"
)

plot_hist_results(
  replicas_to_plot,
  replicas_to_plot$totalBusyTime,
  "total busy-time (hour)", "Total replicas TotalBusyTime for each idletime"
)
plot_hist_results(
  replicas_to_plot[replicas_to_plot$idletime != 0, ],
  replicas_to_plot[replicas_to_plot$idletime != 0, ]$totalBusyTime,
  "total busy-time (hour)", "Total replicas TotalBusyTime for each idletime (excluding idletime zero)"
)

plot_hist_results(
  replicas_to_plot,
  replicas_to_plot$totalBusyTime / replicas_to_plot$totalUptime,
  "total busy-time (hour)", "Total replicas Efficiency for each idletime"
)
plot_hist_results(
  replicas_to_plot[replicas_to_plot$idletime != 0, ],
  replicas_to_plot[replicas_to_plot$idletime != 0, ]$totalBusyTime / replicas_to_plot[replicas_to_plot$idletime != Inf, ]$totalUptime,
  "total busy-time (hour)", "Total replicas Efficiency for each idletime (excluding idletime zero)"
)

plot_hist_results(
  replicas_to_plot,
  replicas_to_plot$replicasCount,
  "number of replicas", "Total number of replicas created for each idletime"
)
plot_hist_results(
  replicas_to_plot[replicas_to_plot$idletime != 0, ],
  replicas_to_plot[replicas_to_plot$idletime != 0, ]$replicasCount,
  "number of replicas", "Total number of replicas created for each idletime (excluding idletime zero)"
)
```



# Load Data For Specific Scenario
```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
results_path <- "/Users/davidquaresma/Desktop/repos/faas-simulator/results_generator"
invoc_file = "_idletime0.0_tlprobp95-invocations.csv"
repl_file = "_idletime0.0_tlprobp95-replicas.csv"
sel_file = "_idletime0.0_tlprobp95-selector.csv"

technique = "Vanilla"
vanilla_invoc = read.csv(paste(results_path, "/", technique, "/", technique, invoc_file, sep=""))
vanilla_invoc <- select(transform(vanilla_invoc, minResponseTime = pmin(responseTime, techniqueResponseTime)), responseTime, techniqueResponseTime, minResponseTime)
vanilla_invoc$responseTimeToEvaluate <- ifelse(vanilla_invoc$minResponseTime != 0, vanilla_invoc$minResponseTime, vanilla_invoc$responseTime)
vanilla_repl = read.csv(paste(results_path, "/", technique, "/", technique, repl_file, sep=""))
vanilla_sel = read.csv(paste(results_path, "/", technique, "/", technique, sel_file, sep=""))

technique = "RequestHedgingDefault"
rh_invoc = read.csv(paste(results_path, "/", technique, "/", technique, invoc_file, sep=""))
rh_invoc <- select(transform(rh_invoc, minResponseTime = pmin(responseTime, techniqueResponseTime)), responseTime, techniqueResponseTime, minResponseTime)
rh_invoc$responseTimeToEvaluate <- ifelse(rh_invoc$minResponseTime != 0, rh_invoc$minResponseTime, rh_invoc$responseTime)
rh_repl = read.csv(paste(results_path, "/", technique, "/", technique, repl_file, sep=""))
rh_sel = read.csv(paste(results_path, "/", technique, "/", technique, sel_file, sep=""))

technique = "RequestHedgingOpt"
rho_invoc = read.csv(paste(results_path, "/", technique, "/", technique, invoc_file, sep=""))
rho_invoc <- select(transform(rho_invoc, minResponseTime = pmin(responseTime, techniqueResponseTime)), responseTime, techniqueResponseTime, minResponseTime)
rho_invoc$responseTimeToEvaluate <- ifelse(rho_invoc$minResponseTime != 0, rho_invoc$minResponseTime, rho_invoc$responseTime)
rho_repl = read.csv(paste(results_path, "/", technique, "/", technique, repl_file, sep=""))
rho_sel = read.csv(paste(results_path, "/", technique, "/", technique, sel_file, sep=""))

technique = "GCI"
gci_invoc = read.csv(paste(results_path, "/", technique, "/", technique, invoc_file, sep=""))
gci_invoc <- select(transform(gci_invoc, minResponseTime = pmin(responseTime, techniqueResponseTime)), responseTime, techniqueResponseTime, minResponseTime)
gci_invoc$responseTimeToEvaluate <- ifelse(gci_invoc$minResponseTime != 0, gci_invoc$minResponseTime, gci_invoc$responseTime)
gci_repl = read.csv(paste(results_path, "/", technique, "/", technique, repl_file, sep=""))
gci_sel = read.csv(paste(results_path, "/", technique, "/", technique, sel_file, sep=""))

azure_input = read.csv(paste("/Users/davidquaresma/Desktop/repos/faas-simulator/azure/", "AzureFunctionsInvocationTraceForTwoWeeksJan2021-final.csv", sep=""))

rm(results_path)
rm(invoc_file)
rm(repl_file)
rm(sel_file)
rm(technique)
```

# ECDF of Latency, Replicas Alive Through Time, Workload
```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
plot_ecdf("Comparison of ECDF Curves of Experiments", data.frame(
  vanilla = vanilla_invoc$responseTimeToEvaluate,
  rh = rh_invoc$responseTimeToEvaluate,
  rho = rho_invoc$responseTimeToEvaluate,
  gci = gci_invoc$responseTimeToEvaluate
), 0, 25, 0, 1, img_name="results-ecdf.png")

plot_replicas_alive(
  bind_rows(vanilla = vanilla_sel, rh = rh_sel, rho = rho_sel, gci = gci_sel, .id = "scenario"),
  scenario_col = "scenario",
  title = "Replicas Active: idletime15.0, tlprobp95"
)
plot_replicas_alive(
  bind_rows(gci = gci_sel, .id = "scenario"),
  scenario_col = "scenario",
  title = "Replicas Active: idletime15.0, tlprobp95"
)
plot_replicas_alive(
  bind_rows(rh = rh_sel, rho = rho_sel, .id = "scenario"),
  scenario_col = "scenario",
  title = "Replicas Active: idletime15.0, tlprobp95"
)
plot_replicas_alive(
  bind_rows(rho = rho_sel, .id = "scenario"),
  scenario_col = "scenario",
  title = "Replicas Active: idletime15.0, tlprobp95"
)
plot_replicas_alive(
  bind_rows(vanilla = vanilla_sel, .id = "scenario"),
  scenario_col = "scenario",
  title = "Replicas Active: idletime15.0, tlprobp95"
)

azure_input$target_timestamp = azure_input$start_timestamp
plot_requests_workload(azure_input, title="Invocations Starting At")
azure_input$target_timestamp = azure_input$end_timestamp
plot_requests_workload(azure_input, title="Invocations Ending At")
```

# Boxplot Visual Test
```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
df_gci_to_boxplot = data.frame(scenario = "gci", responseTime = gci$responseTimeToEvaluate)
df_rh_to_boxplot = data.frame(scenario = "rh", responseTime = rh$responseTimeToEvaluate)
df_rho_to_boxplot = data.frame(scenario = "rho", responseTime = rho$responseTimeToEvaluate)
df_van_to_boxplot = data.frame(scenario = "vanilla", responseTime = vanilla$responseTimeToEvaluate)
boxplot_plot("Boxplot for response time", df_gci_to_boxplot, df_rh_to_boxplot, df_rho_to_boxplot, df_van_to_boxplot, c(0, 5))
```

# Playground For Exploring Funcs
```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
azure_input = read.csv(paste("/Users/davidquaresma/Desktop/repos/faas-simulator/azure/", "AzureFunctionsInvocationTraceForTwoWeeksJan2021-final.csv", sep=""))

tmp <- azure_input %>%
  group_by(func) %>%
  mutate(jaja = quantile(duration, probs = 0.5, na.rm = TRUE)) %>%
  ungroup()


# check app functions rows
length(unique(azure_input$func))
azure_input %>% group_by(func) %>% summarise(count = n()) %>% arrange(desc(count))

# check apps with no zero duration
length(unique(azure_input[azure_input$duration != 0, ]$func))
azure_input[azure_input$duration != 0, ] %>% group_by(func) %>% summarise(count = n())%>% arrange(desc(count))

# check for specific app
azure_input_filter = filter(azure_input, app == "a594f92f84072b4cd031fe5283d1781a6e98f430696dec0a8e3b02eadb5fc0b8")
length(unique(azure_input_filter$func))
azure_input_filter %>% group_by(func) %>% summarise(count = n())%>% arrange(desc(count))
```

# Playground Plotting Funcs
```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
# Load required libraries
library(dplyr)
library(ggplot2)
library(tidyr)

# Define your function IDs for easier reference
func_ids <- c(
  "func1" = "89d488538f940c98367ff572230106d1089868bdd379d9e2b9755b679dc186d2",
  "func2" = "b89efb5e9d1b7e5900ef441b098d4c8b01600af5e673a9f9d607b3598f0fe548",
  "func3" = "c098bb74acb70a0ea1bce98a7090169f3be59a0758389a403d77592aa56ce596",
  "func4" = "1bfbf6e1f849d22a0ece669507eb055525edf6929f273b999d865d52ea086a82",
  "func5" = "1cf618f9ee318fecbc31aa059ded8328581b9a9b092f1069b9f7679b6f89e52e",
  "func6" = "e5298aafdbabecd1465ab0eeb24d7633ac7de0284f7ee075209b119c297a3622"
)

# Method 1: Box Plot Comparison
# Prepare data for plotting
duration_data <- data.frame()
for(i in 1:length(func_ids)) {
  func_data <- filter(azure_input, func == func_ids[i])
  if(nrow(func_data) > 0) {
    temp_df <- data.frame(
      Function = names(func_ids)[i],
      Duration = func_data$duration
    )
    duration_data <- rbind(duration_data, temp_df)
  }
}

# Create box plot
p1 <- ggplot(duration_data, aes(x = Function, y = Duration, fill = Function)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, alpha = 0.6) +
  labs(title = "Duration Comparison Across Functions",
       subtitle = "Box plots showing distribution of execution times",
       x = "Function",
       y = "Duration") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none")

print(p1)

# Method 2: Violin Plot (shows distribution shape)
p2 <- ggplot(duration_data, aes(x = Function, y = Duration, fill = Function)) +
  geom_violin() +
  geom_boxplot(width = 0.1, alpha = 0.8) +
  labs(title = "Duration Distribution Comparison",
       subtitle = "Violin plots showing probability density of execution times",
       x = "Function",
       y = "Duration") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none")

print(p2)

# Method 3: Summary Statistics Comparison
summary_stats <- duration_data %>%
  group_by(Function) %>%
  summarise(
    Count = n(),
    Mean = mean(Duration, na.rm = TRUE),
    Median = median(Duration, na.rm = TRUE),
    SD = sd(Duration, na.rm = TRUE),
    Min = min(Duration, na.rm = TRUE),
    Max = max(Duration, na.rm = TRUE),
    .groups = 'drop'
  )

print("Summary Statistics:")
print(summary_stats)

# Method 4: Bar plot of mean durations with error bars
p3 <- ggplot(summary_stats, aes(x = Function, y = Mean, fill = Function)) +
  geom_col() +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), 
                width = 0.2, alpha = 0.7) +
  labs(title = "Mean Duration Comparison",
       subtitle = "Error bars show ± 1 standard deviation",
       x = "Function",
       y = "Mean Duration") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none")

print(p3)

# Method 5: Density plots overlaid
p4 <- ggplot(duration_data, aes(x = Duration, fill = Function)) +
  geom_density(alpha = 0.6) +
  labs(title = "Duration Density Comparison",
       subtitle = "Overlapping density curves for each function",
       x = "Duration",
       y = "Density") +
  theme_minimal() +
  facet_wrap(~Function, scales = "free")

print(p4)

# Alternative: Single plot with all densities
p5 <- ggplot(duration_data, aes(x = Duration, color = Function)) +
  geom_density(size = 1.2) +
  labs(title = "Duration Density Comparison - Overlay",
       subtitle = "All function densities on same plot",
       x = "Duration",
       y = "Density") +
  theme_minimal()

print(p5)
```

