---
title: "Synthetic Deliveries"
author: "David Ferreira Quaresma (david.quaresma@ccc.ufcg.edu.br)"
date: "set, 2025"
output: pdf_document
---

```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
source("utils.R")
```

# Load Data
## Load Generated
```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
generated_input = read.csv(paste(
  "/Users/davidquaresma/Desktop/repos/faas-simulator/traces/generator/",
  "all_generated_preprocessed-final.csv", sep="")
)
#generated_input$time_readable <- as.POSIXct(generated_input$target_timestamp, origin = "2021-01-31", tz = "UTC")
```

## Load Simulated
```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
load_sim_results <- function(file_sufix) {
  sim_results_path="/Users/davidquaresma/Desktop/repos/faas-simulator/sim_results/generator/baseline/"
  technique = "baseline"
  parameters = "_idletimeINF_tlprobp95"
 
  baseline_inf_input = read.csv(paste(sim_results_path, technique, parameters, file_sufix, sep=""))
  parameters = "_idletime900.0_tlprobp95"
  baseline_15min_input = read.csv(paste(sim_results_path, technique, parameters, file_sufix, sep=""))
  
  sim_results_path="/Users/davidquaresma/Desktop/repos/faas-simulator/sim_results/generator/simplehr/"
  technique = "simplehr"
  parameters = "_idletimeINF_tlprobp95"
  simplehr_inf_input = read.csv(paste(sim_results_path, technique, parameters, file_sufix, sep=""))
  parameters = "_idletime900.0_tlprobp95"
  simplehr_15min_input = read.csv(paste(sim_results_path, technique, parameters, file_sufix, sep=""))
  
  rm(sim_results_path)
  rm(technique)
  rm(parameters)
  rm(file_sufix)
  
  return(
    list(
      baseline_inf_input = baseline_inf_input,
      baseline_15min_input = baseline_15min_input,
      simplehr_inf_input = simplehr_inf_input,
      simplehr_15min_input = simplehr_15min_input
    )
  )
}

file_sufix = "-invocations.csv"
loaded = load_sim_results(file_sufix)
baseline_inf_input = loaded$baseline_inf_input
baseline_15min_input = loaded$baseline_15min_input
simplehr_inf_input = loaded$simplehr_inf_input
simplehr_15min_input = loaded$simplehr_15min_input

baseline_inf_input$responseTimeToEvaluate = calculate_responseTimeToEvaluate(baseline_inf_input)$responseTimeToEvaluate
baseline_15min_input$responseTimeToEvaluate = calculate_responseTimeToEvaluate(baseline_15min_input)$responseTimeToEvaluate
simplehr_inf_input$responseTimeToEvaluate = calculate_responseTimeToEvaluate(simplehr_inf_input)$responseTimeToEvaluate
simplehr_15min_input$responseTimeToEvaluate = calculate_responseTimeToEvaluate(simplehr_15min_input)$responseTimeToEvaluate
```

# Plot Arrivals Rate + Cullen and Frey Graph
```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
library(fitdistrplus)

functions_to_plot <- c(
  "constant-bernoulli-func",
  "constant-logNormal-func",
  "constant-weibull-func"
)
titles <- c(
  "bernoulli",
  "logNormal",
  "weibull"
)

for (i in 1:length(functions_to_plot)) {
  generated_input_filtered = filter(generated_input, func == functions_to_plot[i])
  print(plot_requests_workload(generated_input_filtered, title=paste("Invocations for Function ", titles[i], sep="")))

  #desc_dist <- descdist(generated_input_filtered %>% pull(duration), discrete = FALSE, boot = 500)
}
rm(generated_input_filtered)
```

# Histograms for Latency:
## Sanity Tests comparing generated traces (Bernoulli & LogNormal) to simulated baseline at idletime INF
```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
for (i in 1:length(functions_to_plot)) {
  call_histograms(
    filter(generated_input, func == functions_to_plot[i])$duration,
    filter(baseline_inf_input, funcID == functions_to_plot[i])$responseTimeToEvaluate,
    paste(titles[i], "trace input", sep=" "),
    paste(titles[i], "baseline sim", sep=" "),
    "Generated vs Simulated: Sanity Check",
    c("#53B0E6", "#FFB86B", "#0000CC", "#CC5500", "darkblue", "saddlebrown")
  )
}
```

## Simulated: SimpleHR vs Baseline with idletime as INF
```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
for (i in 1:length(functions_to_plot)) {
  call_histograms(
    filter(baseline_inf_input, funcID == functions_to_plot[i])$responseTimeToEvaluate,
    filter(simplehr_inf_input, funcID == functions_to_plot[i])$responseTimeToEvaluate,
    paste(titles[i], "baseline sim", sep=" "),
    paste(titles[i], "simplehr sim", sep=" "),
    "Generated vs Simulated for Idletime INF",
    c("#FF6B6B", "#4ECDC4", "#CC0000", "#006B5B", "darkred", "darkslategray")
  )
}
```

## Simulated: SimpleHR vs Baseline with idletime as ZERO
```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
for (i in 1:length(functions_to_plot)) {
  call_histograms(
    filter(baseline_15min_input, funcID == functions_to_plot[i])$responseTimeToEvaluate,
    filter(simplehr_15min_input, funcID == functions_to_plot[i])$responseTimeToEvaluate,
    paste(titles[i], "baseline sim", sep=" "),
    paste(titles[i], "simplehr sim", sep=" "),
    "Generated vs Simulated for Idletime 15min",
    c("#FF6B6B", "#4ECDC4", "#CC0000", "#006B5B", "darkred", "darkslategray")
  )
}
```
## Total Function Latency Reduction Table
```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
scenario <- c()
baseline_latency <- c()
simplehr_latency <- c()
percentage <- c()
for (i in 1:length(functions_to_plot)) {
  baseline_response = filter(baseline_inf_input, funcID == functions_to_plot[i])$responseTimeToEvaluate
  simplehr_response = filter(simplehr_inf_input, funcID == functions_to_plot[i])$responseTimeToEvaluate
  scenario <- append(scenario, paste("func", titles[i], "idletime-INF", sep="-"))
  baseline_latency <- append(baseline_latency, sum(baseline_response))
  simplehr_latency <- append(simplehr_latency, sum(simplehr_response))
  percentage <- append(percentage, (1-sum(simplehr_response)/sum(baseline_response))*100)
  #print(summary_table(baseline_response, "baseline INF", simplehr_response,"simplehr INF"))

  baseline_response = filter(baseline_15min_input, funcID == functions_to_plot[i])$responseTimeToEvaluate
  simplehr_response = filter(simplehr_15min_input, funcID == functions_to_plot[i])$responseTimeToEvaluate
  scenario <- append(scenario, paste("func", titles[i], "idletime-15min", sep="-"))
  baseline_latency <- append(baseline_latency, sum(baseline_response))
  simplehr_latency <- append(simplehr_latency, sum(simplehr_response))
  percentage <- append(percentage, (1-sum(simplehr_response)/sum(baseline_response))*100)
  #print(summary_table(baseline_response, "baseline 15min", simplehr_response,"simplehr 15min"))
}
rm(baseline_response)
rm(simplehr_response)

total_latency_table <- data.frame(scenario, baseline_latency, simplehr_latency, percentage)
print(total_latency_table)
rm(baseline_latency)
rm(simplehr_latency)
rm(percentage)
rm(total_latency_table)

rm(scenario)
```

# Replicas Evaluation
## Load Provisioner's sim data
```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
file_sufix = "-provisioners.csv"
loaded = load_sim_results(file_sufix)
baseline_inf_input = loaded$baseline_inf_input
baseline_15min_input = loaded$baseline_15min_input
simplehr_inf_input = loaded$simplehr_inf_input
simplehr_15min_input = loaded$simplehr_15min_input
```

# Plot Replicas Alive
```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
for (i in 1:length(functions_to_plot)) {
  print(
    plot_replicas_alive(
      bind_rows(
        baseline_inf = filter(baseline_inf_input, funcID == functions_to_plot[i]),
        simplehr_inf = filter(simplehr_inf_input, funcID == functions_to_plot[i]),
        baseline_15min = filter(baseline_15min_input, funcID == functions_to_plot[i]),
        simplehr_15min = filter(simplehr_15min_input, funcID == functions_to_plot[i]),
        .id = "scenario"
      ),
      c("baseline_inf", "simplehr_inf", "baseline_15min", "simplehr_15min"),
      scenario_col = "scenario",
      title = paste(titles[i], ": Replicas Active for Baseline vs SimpleHR", sep="")
    )
  )
}
```

## Load Replicas sim data
```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
file_sufix = "-replicas.csv"
loaded = load_sim_results(file_sufix)
baseline_inf_input = loaded$baseline_inf_input
baseline_15min_input = loaded$baseline_15min_input
simplehr_inf_input = loaded$simplehr_inf_input
simplehr_15min_input = loaded$simplehr_15min_input
```

## Table totals for uptime, busytime and ratio.
```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
scenario <- c()
baseline_sumuptime <- c()
simplehr_sumuptime <- c()
baseline_sumbusytime <- c()
simplehr_sumbusytime <- c()
baseline_effy <- c()
simplehr_effy <- c()
for (i in 1:length(functions_to_plot)) {
  scenario <- append(scenario, paste("func", titles[i], "idletime-INF", sep="-"))
  baseline_total = sum(filter(baseline_inf_input, funcID == functions_to_plot[i])$upTime)
  simplehr_total = sum(filter(simplehr_inf_input, funcID == functions_to_plot[i])$upTime)
  baseline_sumuptime <- append(baseline_sumuptime, baseline_total)
  simplehr_sumuptime <- append(simplehr_sumuptime, simplehr_total)
  baseline_busy = sum(filter(baseline_inf_input, funcID == functions_to_plot[i])$busyTime)
  simplehr_busy = sum(filter(simplehr_inf_input, funcID == functions_to_plot[i])$busyTime)
  baseline_sumbusytime <- append(baseline_sumbusytime, baseline_busy)
  simplehr_sumbusytime <- append(simplehr_sumbusytime, simplehr_busy)
  baseline_effy <- append(baseline_effy, baseline_busy/baseline_total*100)
  simplehr_effy <- append(simplehr_effy, simplehr_busy/simplehr_total*100)

  scenario <- append(scenario, paste("func", titles[i], "idletime-15min", sep="-"))
  baseline_total = sum(filter(baseline_15min_input, funcID == functions_to_plot[i])$upTime)
  simplehr_total = sum(filter(simplehr_15min_input, funcID == functions_to_plot[i])$upTime)
  baseline_sumuptime <- append(baseline_sumuptime, baseline_total)
  simplehr_sumuptime <- append(simplehr_sumuptime, simplehr_total)
  baseline_busy = sum(filter(baseline_15min_input, funcID == functions_to_plot[i])$busyTime)
  simplehr_busy = sum(filter(simplehr_15min_input, funcID == functions_to_plot[i])$busyTime)
  baseline_sumbusytime <- append(baseline_sumbusytime, baseline_busy)
  simplehr_sumbusytime <- append(simplehr_sumbusytime, simplehr_busy)
  baseline_effy <- append(baseline_effy, baseline_busy/baseline_total*100)
  simplehr_effy <- append(simplehr_effy, simplehr_busy/simplehr_total*100)
  
}
rm(baseline_total)
rm(baseline_busy)
rm(simplehr_total)
rm(simplehr_busy)

total_effy_table <- data.frame(
  scenario = scenario,
  baseline_busy = baseline_sumbusytime,
  simplehr_busy = simplehr_sumbusytime,
  baseline_up = baseline_sumuptime,
  simplehr_up = simplehr_sumuptime,
  baseline_effy = baseline_effy,
  simplehr_effy = simplehr_effy
)
print(total_effy_table)

rm(scenario)
rm(baseline_sumuptime)
rm(simplehr_sumuptime)
rm(baseline_sumbusytime)
rm(simplehr_sumbusytime)
rm(baseline_effy)
rm(simplehr_effy)
rm(percentage)
```
